%!TEX root = ../main.tex
\begin{abstract}
In a corporate context where rapid and accurate information analysis is crucial to improving operational performance and supporting data-driven strategic decisions, this thesis focuses on the design and implementation of a \acf{BI} system and a Data Lake for the company UNOX S.p.A., leveraging the technologies provided by the \acf{AWS} platform.

The BI system developed allows the collection and analysis of data from various sources, helping to reduce inefficiencies, flag potential issues, identify new revenue streams, and pinpoint areas for future growth. Through the creation of a centralized Data Lake and the automation of data integration and analysis processes, it became possible to optimize the management of corporate information, providing a comprehensive and detailed view of business performance.

The system was designed to be easily accessible to various company teams, including Research and Development, IT, and other technical departments, thanks to intuitive tools such as AWS QuickSight. These tools enable a simple and visual interaction with the data without requiring specific knowledge of DBMS or query languages. This approach has made data more accessible at all company levels, promoting greater autonomy in their analysis.

The implementation made use of AWS components such as Amazon S3, Glue, Athena and QuickSight, ensuring scalable, secure, and fully automated data management. The final result is an integrated \acl{BI} system that significantly reduces the time required for analysis and reporting, enhancing decision-making capabilities and promoting a data-driven corporate culture.
\end{abstract}